Reproducible Research in R: A Tutorial on how to Do the Same Thing More Than Once

### 2021-11-16 manuscript.Rmd
move to footnote closes #273 closes #274

Naturally we did not access the data when we initially wrote this code.
We therefore did not know the exact format the data would have.
This means that we did need to change our preregistration after accessing the data to include i.e. the recoding of gender (lines 17-22) and the items (lines 23-26).
We invite the reader to evaluate the changes we made to the preregistered code on [GitHub](https://github.com/aaronpeikert/repro-tutorial/compare/v0.0.1.1-prereg..main#diff-e21a8fa2e44b297dfefef329a6ef56d283488d467c4b4ffe2a014111e52a170b).

>>>>

Naturally we did not access the data when we initially wrote this code.
We therefore did not know the exact format the data would have.
This means that we did need to change our preregistration after accessing the data to include i.e. the recoding of gender (lines 17-22) and the items (lines 23-26).[^prereg-changes]

[^prereg-changes]: We invite the reader to evaluate the changes we made to the preregistered code.
Either on [GitHub](https://github.com/aaronpeikert/repro-tutorial/compare/v0.0.1.1-prereg...main) → "Files changed" or directly in Git with `git diff v0.0.1.1-prereg preregistration.Rmd`.
